Towards a Machine Learning approach for Aggregate Computing

### 2021-11-04 paper-2021-woa-ac-ml.tex
change style according to alpaca requirements

%% The first command in your LaTeX source must be the \documentclass command.
%%
%% Options:
%% hf: enable header and footer.
\documentclass[
  twocolumn,
  % hf
]{ceurart}
\usepackage{tcolorbox}
\usepackage[colorinlistoftodos,prependcaption]{todonotes}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{minted}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{systeme}
\usepackage{cleveref}

\setminted{frame=single}
\sloppy

\begin{document}
\conference{ - X - }

\title{Towards a Machine Learning approach for Aggregate Computing} %% or Towards a Machine Learning approach for Aggregate Computing

\author[1]{Gianluca Aguzzi}[%
 orcid=todo,
 email=gianluca.aguzzi@unibo.it,
 url=https://todo/,
]

\author[2]{Roberto Casadei}[%
 orcid=todo,
 email=roby.casadei@unibo.it,
 url=todo,
]

\author[3]{Mirko Viroli}[%
 orcid=todo,
 email=mirko.viroli@unibo.it,
 url=todo,
]
\address[1]{Alma Mater Studiorum - Università di Bologna, Cesena, Italy}
%%%%% LEGENDA FOR NOTES %%%%%
%% RED: constraints
%% YELLOW: suggestions
%% CYAN: todos
%% GREEN: outline
\newcommand{\constraints}[1]{\todo[inline, color=red]{#1}}
\newcommand{\suggestions}[1]{\todo[inline, color=yellow]{#1}}
\newcommand{\todos}[1]{\todo[inline, color=cyan]{#1}}
\newcommand{\outline}[1]{\todo[inline, color=green]{#1}}
%% Utility commands
\newcommand{\hybridaggregate}{\textit{Hybrid Aggregate Computing}}
\newcommand{\round}{\texttt{round}}
\newcommand{\export}{\texttt{export}}
%% Minted helpers
\definecolor{mblue}{rgb}{0.27,0.33,0.53}
\begin{abstract}
\suggestions{}
Artificial intelligence is here to stay. 
 In particular, Deep Learning techniques in the last years outperform 
 hand-craft human solutions in different contexts, ranging from computer vision to videogames.
%
Currently, though, an all-encompassing Deep learning algorithm does not exist, 
 so researchers explore the possibility to apply these techniques in different fields.

@@

On the opposite side, some research lines apply Deep learning (supervised, reinforcement, non-supervised and self-supervised)
 along with CAS. Currently, though, no one gain popularity and solution tend to be application-specific.
%
So, we outline a Machine Learning technique that could be applied in Aggregate Computing, 
 making the possibility to combine specification-based and automatic approaches that can easily scale in application complexity and to any system size.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  Collective-Adaptive System \sep
  Aggregate Computing \sep
  Deep Learning \sep
  Reinforcement Learning \sep
\end{keywords}

\maketitle
\suggestions{Perhaps we could change the narration directly towards "reinforcement learning". I think that I cannot continue to explore multiple solutions..}
\section{Introduction}
Nowadays, computer engineers have to deal with Collective Adaptive Systems (CASs)
 due to the increasing interconnected computational devices placed in ever-changing environments.
 Examples of those include robot swarm, smart cities and augmenting crowds.

@@

\todos{discussion about the result}
\todos{limitations: it does not easily scale with the complex application, it cannot be applied online, it cannot be used in different scenarios}
\todos{future work: integrate deep learning solution, integrate actor-critic method (team learning)}
%%
%% Define the bibliography file to be used
\nocite{*}
\bibliography{biblio}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}

\usepackage{tcolorbox}
\usepackage[colorinlistoftodos,prependcaption]{todonotes}
\usepackage{xcolor}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{minted}
\usepackage{subcaption}
\usepackage[hidelinks]{hyperref}
\usepackage[inline]{enumitem}
\usepackage[T1]{fontenc}
\usepackage{cleveref}
\usepackage{systeme}
\setminted[scala]{fontsize=\scriptsize,baselinestretch=1,bgcolor=white,frame=single}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
  T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\sloppy

\newcommand{\unibo}{\textsc{Alma Mater Studiorum} -- \textit{Università di Bologna}}
\newcommand{\disi}{\textit{Computer Science and Engineering - DISI}}
\newcommand{\scafi}{{ScaFi}}
\newcommand{\scalaloci}{{ScalaLoci}}
\newcommand{\scafiloci}{{ScaFiLoci}}
\newcommand{\scalainline}[1]{\mintinline[fontsize=\small]{scala}{#1}}
%%%%% LEGENDA FOR NOTES %%%%%
%% RED: constraints
%% YELLOW: suggestions
%% CYAN: todos
%% GREEN: outline
\newcommand{\constraints}[1]{\todo[inline, color=red]{#1}}
\newcommand{\suggestions}[1]{\todo[inline, color=yellow]{#1}}
\newcommand{\todos}[1]{\todo[inline, color=cyan]{#1}}
\newcommand{\outline}[1]{\todo[inline, color=green]{#1}}
%% Utility commands
\newcommand{\hybridaggregate}{\textit{Hybrid Aggregate Computing}}
\newcommand{\round}{\texttt{round}}
\newcommand{\export}{\texttt{export}}

\begin{document}

\title{Towards a Machine Learning approach for Aggregate Computing} %% or Towards a Machine Learning approach for Aggregate Computing
\author{\IEEEauthorblockN{
Gianluca Aguzzi\IEEEauthorrefmark{1},
Roberto Casadei\IEEEauthorrefmark{1},
Mirko Viroli\IEEEauthorrefmark{1}
}\\
\IEEEauthorblockA{\IEEEauthorrefmark{1}
\textsc{Alma Mater Studiorum}---Universit\`a di Bologna, Cesena, Italy\\
Email: \{gianluca.aguzzi, roby.casadei, mirko.viroli\}@unibo.it
}}

%% Minted helpers
\definecolor{mblue}{rgb}{0.27,0.33,0.53}
%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
%\begin{keywords}
%  Collective-Adaptive System \sep
%  Aggregate Computing \sep
%  Deep Learning \sep
%  Reinforcement Learning \sep
%\end{keywords}

\maketitle
\begin{abstract}
\suggestions{}
Artificial intelligence is here to stay. 
 In particular, Deep Learning techniques in the last years outperform 
 hand-craft human solutions in different contexts, ranging from computer vision to videogames.
%
Currently, though, an all-encompassing Deep learning algorithm does not exist, 
 so researchers explore the possibility to apply these techniques in different fields.

@@

On the opposite side, some research lines apply Deep learning (supervised, reinforcement, non-supervised and self-supervised)
 along with CAS. Currently, though, no one gain popularity and solution tend to be application-specific.
%
So, we outline a Machine Learning technique that could be applied in Aggregate Computing, 
 making the possibility to combine specification-based and automatic approaches that can easily scale in application complexity and to any system size.
\end{abstract}
\begin{IEEEkeywords}
  Collective-Adaptive System,
  Aggregate Computing,
  Deep Learning,
  Reinforcement Learning
\end{IEEEkeywords}

\suggestions{Perhaps we could change the narration directly towards "reinforcement learning". I think that I cannot continue to explore multiple solutions..}
\section{Introduction}
Nowadays, computer engineers have to deal with Collective Adaptive Systems (CASs)
 due to the increasing interconnected computational devices placed in ever-changing environments.
 Examples of those include robot swarm, smart cities and augmenting crowds.

@@

\todos{discussion about the result}
\todos{limitations: it does not easily scale with the complex application, it cannot be applied online, it cannot be used in different scenarios}
\todos{future work: integrate deep learning solution, integrate actor-critic method (team learning)}
%%
%% Define the bibliography file to be used

\bibliographystyle{IEEEtran}
\bibliography{biblio}
%%
%% If your work has an appendix, this is the place to put it.
\appendix
